\newpage
\thispagestyle{empty}
\section*{Preface}
This Bachelor Thesis represents not only a significant academic challenge but also a deeply personal journey for us. My partner, Ardi Jasari, brought a robust IT background to our project, providing essential technical knowledge that helped us navigate many challenges associated with deep learning applications. Myself, Marcel Avesani, an Industrial Engineering student with a recent specialization in data and service engineering, initially lacked IT skills but was drawn to the world of data science. Together, we share a profound interest in how data, combined with advanced algorithms, can mimic human intelligence. This is particularly significant in the context of these algorithms' potential to influence society by aiding in the detection of misinformation—a topic that has gained immense importance with the rise of social media and the shift from traditional media outlets to decentralized media platforms.
Working on deep learning models to detect misinformation has been incredibly insightful. Technically, it allowed us to deepen our understanding of artificial intelligence, especially in the field of Natural Language Processing. Engaging in a prolonged project like this one has fostered our critical thinking and helped us develop a deeper understanding that goes beyond simply studying theory. Additionally, we gained valuable insights into political debate data and the crucial field of misinformation detection, including the extensive efforts required to maintain information accuracy and reliability.
Furthermore, as partners from different academic backgrounds, we developed effective collaboration strategies that maximized the benefits and outcomes of our study. Our partnership was a thoroughly positive experience; despite the challenges, the work was incredibly fun and rewarding.
Special thanks go to Pius von Däniken and Dr. Jan Deriu, specialists in this topic, who provided us with valuable tips and continuous support throughout our study. Their dedication and assistance were crucial in helping us navigate difficulties and greatly contributed to the success of our work.
